\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 paper.tex
quick fix in abstract

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today ---unit, integration, and stress testing--- are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach significantly improves test coverage and allows us to discover during testing errors that are often caught after deployment.

>>>>

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today --- unit, integration, and stress testing --- are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach significantly improves test coverage and allows us to discover errors during testing that are often caught after deployment.
